The Processing of American Indian/Alaska Native Children through non-Tribal

### 2019-12-21 ms.rmd
git figures started, check on p(fc, inv) > p(fc) cases

@@

investigation_tables<-list()
years<-unique(ncands_first_nat$year)
race_ethn<-unique(ncands_first$race_ethn)
for(i in 1:length(years)){
  for(r in 1:length(race_ethn)){
  investigation_tables[[i]]<-make_life_table(ncands_first_nat %>% 
                  filter(year==years[i]) %>% 
                    filter(race_ethn == race_ethn[r]))
  }
}

investigation_tables<-bind_rows(investigation_tables)

investigation_tables %>% 
  filter(age==17) %>% 
  ggplot(aes(x=year, y = c, color = race_ethn)) +
  geom_line()

@@

### run lifetable by year

subst_tables<-list()
years<-unique(ncands_first_subst_nat$year)
for(i in 1:length(years)){
  subst_tables[[i]]<-make_life_table(ncands_first_subst_nat %>% 
                  filter(year==years[i]))
}

subst_tables<-bind_rows(subst_tables)
```

@@

```{r fctables.pop}

### run lifetable by year
fc_tables<-list()
years<-unique(afcars_first_nat$year)
for(i in 1:length(years)){
  fc_tables[[i]]<-make_life_table(afcars_first_nat %>% 
                  filter(year==years[i]))
}

fc_tables<-bind_rows(fc_tables)
```

@@

```{r}
### among all entries, match on investigation
### question is afcars or ncands on left for join
### likely assymetry
### need first inv date in ncands_xwalk
### to ensure I have inv prior to fc
### to obtain P(inv,entered) where entered occurs after inv

### lifetable for p(inv,entered)

>>>>

ncands_inv<-read_csv("./data/ncands_first_inv.csv") %>% 
  filter(year>=2003, year<2017) %>% 
  filter(age<18) %>% 
  filter(.imp!=0) %>% 
  filter(race_ethn == "AI/AN" | race_ethn == "White")
ncands_sub<-read_csv("./data/ncands_first_sub.csv")%>% 
  filter(year>=2003, year<2017)%>% 
  filter(age<18) %>% 
  filter(.imp!=0) %>% 
  filter(race_ethn == "AI/AN" | race_ethn == "White")
afcars_fc<-read_csv("./data/afcars_first_fc.csv")%>% 
  filter(year>=2003, year<2017)%>% 
  filter(age<18) %>%   
  filter(.imp!=0) %>% 
  filter(race_ethn == "AI/AN" | race_ethn == "White")
afcars_tpr<-read_csv("./data/afcars_tpr.csv")%>% 
  filter(year>=2003, year<2017)%>% 
  filter(age<18) %>% 
  filter(.imp!=0) %>% 
  filter(race_ethn == "AI/AN" | race_ethn == "White")
afcars_non_icwa<-read_csv("./data/afcars_non_icwa.csv")%>% 
  filter(year>=2003, year<2017)%>% 
  filter(age<18) %>% 
  filter(.imp!=0) %>% 
  filter(race_ethn == "AI/AN" | race_ethn == "White")
afcars_fc_inv<-read_csv("./data/afcars_fc_post_inv.csv")%>% 
  filter(year>=2003, year<2017)%>% 
  filter(age<18) %>% 
  filter(.imp!=0) %>% 
  filter(race_ethn == "AI/AN" | race_ethn == "White")
```

@@

investigation_tables<-list()
years<-unique(ncands_inv$year)
race_ethn<-unique(ncands_inv$race_ethn)
index<-1
for(i in 1:5){
  for(j in 1:length(years)){
    for(r in 1:length(race_ethn)){
      temp<-ncands_inv %>% 
        filter(year==years[j])
      temp<-temp %>% 
        filter(race_ethn == race_ethn[r])
      temp<-temp %>% 
        filter(.imp==i)
      investigation_tables[[index]]<-make_life_table(temp)
      index<-index+1
    }
  }
}
investigation_tables<-bind_rows(investigation_tables)

investigation_tables_c<-investigation_tables %>% 
  filter(age==17) %>% 
  group_by(year, race_ethn) %>% 
  summarise(c_mn = mean(c), cmax = max(c), cmin = min(c))

investigation_tables_c %>% 
  ggplot(aes(x=year, y = c_mn, 
             fill = race_ethn,
             group = race_ethn,
             ymin = cmin, ymax = cmax)) +
  geom_ribbon(alpha = .5) + 
  geom_line(aes(color = race_ethn)) + 
  xlab("Year") + 
  ylab("Proportion with screened-in report before age 18")

@@

### run lifetable by year
subst_tables<-list()
years<-unique(ncands_sub$year)
race_ethn<-unique(ncands_sub$race_ethn)
index<-1
for(i in 1:5){
  for(j in 1:length(years)){
    for(r in 1:length(race_ethn)){
      temp<-ncands_sub %>% 
        filter(year==years[j])
      temp<-temp %>% 
        filter(race_ethn == race_ethn[r])
      temp<-temp %>% 
        filter(.imp==i)
      subst_tables[[index]]<-make_life_table(temp)
      index<-index+1
    }
  }
}
subst_tables<-bind_rows(subst_tables)

subst_tables_c<-subst_tables %>% 
  filter(age==17) %>% 
  group_by(year, race_ethn) %>% 
  summarise(c_mn = mean(c), cmax = max(c), cmin = min(c))

subst_tables_c %>% 
  ggplot(aes(x=year, y = c_mn, 
             fill = race_ethn,
             group = race_ethn,
             ymin = cmin, ymax = cmax)) +
  geom_ribbon(alpha = .5) + 
  geom_line(aes(color = race_ethn)) + 
  xlab("Year") + 
  ylab("Proportion with substantiation before age 18")
```

@@

```{r fctables.pop}
fc_tables<-list()
years<-unique(afcars_fc$year)
race_ethn<-unique(afcars_fc$race_ethn)
index<-1
for(i in 1:5){
  for(j in 1:length(years)){
    for(r in 1:length(race_ethn)){
      temp<-afcars_fc %>% 
        filter(year==years[j])
      temp<-temp %>% 
        filter(race_ethn == race_ethn[r])
      temp<-temp %>% 
        filter(.imp==i)
      fc_tables[[index]]<-make_life_table(temp)
      index<-index+1
    }
  }
}
fc_tables<-bind_rows(fc_tables)

fc_tables_c<-fc_tables %>% 
  filter(age==17) %>% 
  group_by(year, race_ethn) %>% 
  summarise(c_mn = mean(c), cmax = max(c), cmin = min(c))

fc_tables_c %>% 
  ggplot(aes(x=year, y = c_mn, 
             fill = race_ethn,
             group = race_ethn,
             ymin = cmin, ymax = cmax)) +
  geom_ribbon(alpha = .5) + 
  geom_line(aes(color = race_ethn)) + 
  xlab("Year") + 
  ylab("Proportion ever in foster care before age 18")
```

@@

```{r}
fc_post_inv_tables<-list()
years<-unique(afcars_fc_inv$year)
race_ethn<-unique(afcars_fc_inv$race_ethn)
index<-1
for(i in 1:5){
  for(j in 1:length(years)){
    for(r in 1:length(race_ethn)){
      temp<-afcars_fc_inv %>% 
        filter(year==years[j])
      temp<-temp %>% 
        filter(race_ethn == race_ethn[r])
      temp<-temp %>% 
        filter(.imp==i)
      fc_post_inv_tables[[index]]<-make_life_table(temp)
      index<-index+1
    }
  }
}
fc_post_inv_tables<-bind_rows(fc_post_inv_tables)

fc_post_inv_tables_c<-fc_post_inv_tables %>% 
  filter(age==17) %>% 
  group_by(year, race_ethn) %>% 
  summarise(c_mn = mean(c), cmax = max(c), cmin = min(c))

fc_post_inv_tables_c %>% 
  ggplot(aes(x=year, y = c_mn, 
             fill = race_ethn,
             group = race_ethn,
             ymin = cmin, ymax = cmax)) +
  geom_ribbon(alpha = .5) + 
  geom_line(aes(color = race_ethn)) + 
  xlab("Year") + 
  ylab("Proportion with foster care entry after screened-in report")
